Something About Ground Based Asteroseismology

### 2017-09-18 paper/aldebaran.tex
theta cyg

The \kepler detector saturates for stars brighter than the $\sim~11^\text{th}$ magnitude. Nevertheless, the excess flux deposited in a saturated pixel spills conservatively up and down the pixel column, such that it is possible to sum this `bleed column' for bright stars and still obtain precise photometry, such as was done for the brightest star in the nominal \kepler mission, $\theta$~Cyg \citep{} ($V = 4.48$). There are two main reasons why this is not possible for all bright stars in general. First, because the downlink bandwidth from \kepler is very limited, it is often not desirable to download the large pixel stamps as are required for such bright stars; these must be even larger in \ktwo to account for the reduced image stability. Second, if the bleed column for a sufficiently bright star reaches the edge of the chip, flux spills over and is not conserved, imposing a hard brightness limit that depends on the distance to the detector edge. 
Collateral `smear' data, which are collected to help calibrate the photometric bias from stars sharing the same column as a target, can be used to reconstruct light curves for un-downloaded bright stars and thereby avoid bandwidth constraints \citep{k2smear}, but these data are still rendered unusable if the bleed column falls off the edge of the chip and contaminates the smear rows.

>>>>

The \kepler detector saturates for stars brighter than the $\sim~11^\text{th}$ magnitude. Nevertheless, the excess flux deposited in a saturated pixel spills conservatively up and down the pixel column, such that it is possible to sum this `bleed column' for bright stars and still obtain precise photometry, such as was done for the brightest star in the nominal \kepler mission, $\theta$~Cyg \citep{guzik2011,thetacygwhite,guzik2016} ($V = 4.48$). There are two main reasons why this is not possible for all bright stars in general. First, because the downlink bandwidth from \kepler is very limited, it is often not desirable to download the large pixel stamps as are required for such bright stars; these must be even larger in \ktwo to account for the reduced image stability. Second, if the bleed column for a sufficiently bright star reaches the edge of the chip, flux spills over and is not conserved, imposing a hard brightness limit that depends on the distance to the detector edge. 
Collateral `smear' data, which are collected to help calibrate the photometric bias from stars sharing the same column as a target, can be used to reconstruct light curves for un-downloaded bright stars and thereby avoid bandwidth constraints \citep{k2smear}, but these data are still rendered unusable if the bleed column falls off the edge of the chip and contaminates the smear rows.
